\documentclass[12pt]{article}

\author{Rose Xu}
\date{\today}

\begin{document}
\maketitle

This is the body of latex hola hell yeah

Engineering 100.100  Wynarsky/Hildinger
Fall 2015

Individual Writing 1: Brief Technical Description (20 points) - Due Sept. 10, 2015

Purpose: This assignment has two primary purposes: (1) to get you started

exploring a topic that interests you and (2) to give you the opportunity to show me

your current understanding of technical writing and the professional presentation
of documents.

Task: Do some preliminary research on an orthopedic implant or an implantable
medical device that you find interesting. Then, on the basis of your research, write a
brief technical description of the device or system in which you introduce and
explain the device to a general reader. Your description should be sufficient to
enable a non-specialist to understand the purpose, form and function of the device.
Thus you will need to provide background information and explain the technical
aspects of the device very clearly. You may use graphics to support your description.

Be sure to document and credit the sources that you use. For documentation, APA
style is preferable (some help on that is posted on the CTools site), but for this
assignment only you may use any standard system. You may use the Sweetland
Writing Center for help with this assignment, if you wish; if you do, be sure to
indicate that in your references.

Add thic Hnnnr Plpd op. at the end of vour document: I have neitherqiven nor

\end{document}

